Learning a functional distance between organizations with unsupervised embeddings of scientific mobility

### 2020-07-24 paper/current/main.tex

Neural embeddings offer a novel, data-driven solution for learning an effective and robust functional distance between places based on trajectory data.
By virtue of being data-driven, and by the nature of neural embedding, it encodes the complex and multi-faceted nature of mobility. 
Here, we demonstrated how the embedding space encodes various aspects of scientific mobility, such as the  global and regional geography, national shared languages, and the hierarchy of organizational prestige, even without explicit information of these factors.
While scientific mobility is used as a case study, this approach can be broadly applied to other kinds of mobility data, such as general human migration, transit-network mobility, and more.
Moreover, this approach can be used to learn a functional distance between entities for which no geographic analog exists, such as between occupational categories based on individual's career trajectories. 
In addition to providing a functional distance that supports modeling and predicting mobility patterns, the unique structure of the neural embedding space is amenable to a range of unique applications for studying mobility. 
As we have shown allows the visualization of the complex structure of scientific mobility at high resolution across multiple scales, providing the largest and most detailed map of global scientific mobility to date. 
Other techniques, such as SemAxis~\autocite{an2018semaxis}, also allow us to quantify abstract notions in mobility such as academic prestige, and can also be generalized to other abstract axes.
Investigation of the structure of the embedding space, such as the vector size, reveals unique and universal patterns based on organization's size and connectedness, and could contribute to deeper understandings of scientific mobility. 
Neural embedding opens the door for new approaches to represent and study scientific mobility, and also mobility more generally.

>>>>

Neural embeddings offer a novel, data-driven solution for learning an effective and robust functional distance between places based on trajectory data.
By virtue of being data-driven, and by the nature of neural embedding, it encodes the complex and multi-faceted nature of mobility. 
Here, we demonstrated how the embedding space encodes various aspects of scientific mobility, such as the global and regional geography, national shared languages, and the hierarchy of organizational prestige, even without explicit information on these factors.
While scientific mobility is used as a case study, this approach can be broadly applied to other kinds of mobility data, such as general human migration, transit-network mobility, and more.
Moreover, this approach can be used to learn a functional distance between entities for which no geographic analog exists, such as between occupational categories based on individual's career trajectories. 
In addition to providing a functional distance that supports modeling and predicting mobility patterns, the unique structure of the neural embedding space is amenable to a range of unique applications for studying mobility. 
As we have shown, the embedding space allows the visualization of the complex structure of scientific mobility at high resolution across multiple scales, providing the largest and most detailed map of global scientific mobility to date. 
Other techniques, such as SemAxis~\autocite{an2018semaxis}, also allow us to quantify abstract notions in mobility such as academic prestige, and can also be generalized to other abstract axes.
Investigation of the structure of the embedding space, such as the vector size, reveals unique and universal patterns based on organization's size and connectedness and could contribute to deeper understandings of scientific mobility. 
Neural embedding opens the door for new approaches to represent and study scientific mobility, and also mobility more generally.
